\ttitle

### 2014-01-20 Appendices/AppendixA-Results.tex
Updates

\begin{table}
  \centering
  \caption[Results real world runs]{Parameter settings and results of the real-world data sets.}
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c|}
    \cline{2-8}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 \\
    \hline
    Window length & 50 & 50 & 50 & 50 & 50 & 50 & 50 \\
    \hline
    Sigma of \gls{rbf} & 13 & 13 & 13 & 13 & 13 & 4 & 13 \\
    \hline
    High threshold & 1.2 & 1.5 & 1.1 & 1.3 & 1.2 & 1.7 & 1.3 \\
    \hline
    Low threshold & 0.8 & 0.8 & 0.7 & 0.7 & 0.8 & 0.6 & 0.6 \\
    \hline
    $\delta$ (s) & 0.7 & 0.85 & 0.6 & 0.7 & 1 & 0.8 & 1 \\
    \hline
    \hline
    $\gamma(Y)$ & 0.1 & 0.05 & 0 & 0.2 & 0 & 0.48 & 0 \\
    \hline
    $d_{avg}$ & 0.52 & 0.83 & 0.92 & 1.26 & 1.05 & 0.92 & 0.47 \\
    \hline
    $std(d_{avg})$ & 0.29 & 0.55 & 0.75 & 1.67 & 0.78 & 0.92 & 0.52 \\
    \hline
  \end{tabulary}
  \label{tab:results_real_world}
\end{table}

>>>>

\begin{table}
  \centering
  \caption[Results real world runs]{Parameter settings and results of the real-world data sets.
  The table shows the \gls{far} $\gamma$, average delay $d_{avg}$ and its spread, using the standard deviation.
  Low values for the results are better.}
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c|}
    \cline{2-8}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 \\
    \hline
    Window length & 50 & 50 & 50 & 50 & 50 & 50 & 50 \\
    \hline
    Sigma of \gls{rbf} & 13 & 13 & 13 & 13 & 13 & 4 & 13 \\
    \hline
    High threshold & 1.2 & 1.5 & 1.1 & 1.3 & 1.2 & 1.7 & 1.3 \\
    \hline
    Low threshold & 0.8 & 0.8 & 0.7 & 0.7 & 0.8 & 0.6 & 0.6 \\
    \hline
    $\delta$ (s) & 0.7 & 0.85 & 0.6 & 0.7 & 1 & 0.8 & 1 \\
    \hline
    \hline
    $\gamma(Y)$ & 0.1 & 0.05 & 0 & 0.2 & 0 & 0.48 & 0 \\
    \hline
    $d_{avg}$ & 0.52 & 0.83 & 0.92 & 1.26 & 1.05 & 0.92 & 0.47 \\
    \hline
    $std(d_{avg})$ & 0.29 & 0.55 & 0.75 & 1.67 & 0.78 & 0.92 & 0.52 \\
    \hline
  \end{tabulary}
  \label{tab:results_real_world}
\end{table}

### 2014-01-20 Chapters/Chapter4/data_gathering.tex
Move results Chapter 6 to Appendix'
Updates

For the experiments we used a smartphone with inertial sensors as recording device.
The activities were recorded using a free \textsc{Android} application \cite{sensorlogger}.
This application was chosen for its convenient data format of the sensor recording and its regularity of the sampling interval.
Table~\ref{tab:recorded_metrics} lists all the recorded metrics.
For our experiments we used the data for the accelerometer, magnetic field and rotation.

We implemented our algorithm in \textsc{MATLAB}.
For the \gls{svdd} model construction phase we used the \textsc{dd\_tools} library by Tax \cite{Ddtools2013}, which depends on the \textsc{PR\_tools} package, originating from the book by Van Der Heijden \etal \cite{van2005classification}.
Alternatively, the widely used \textsc{LibSVM} \cite{chang2011libsvm} add-on for the \gls{svdd} algorithm by Chang \etal \cite{changrevisit} can be used.

>>>>

For the experiments we used a smartphone with inertial sensors as recording device.
The activities were recorded using a free \textsc{Android} application \textsc{Sensor Logger}\footnote{https://play.google.com/store/apps/details?id=
com.kzs6502.sensorlogger}.
This application was chosen for its convenient data format of the sensor recording and its regularity of the sampling interval.
Table~\ref{tab:recorded_metrics} lists all the recorded metrics.
For our experiments we used the data for the accelerometer, magnetic field and rotation.

We implemented our algorithm in \textsc{Matlab}.
For the \gls{svdd} model construction phase we used the \textsc{dd\_tools} library by Tax \cite{Ddtools2013}, which depends on the \textsc{PR\_tools} package, originating from the book by Van Der Heijden \etal \cite{van2005classification}.
Alternatively, the widely used \textsc{LibSVM} \cite{chang2011libsvm} add-on for the \gls{svdd} algorithm by Chang \etal \cite{changrevisit} can be used.

### 2014-01-20 Chapters/Chapter5/results.tex
Chapter 6 run order
Updates

% !TEX root = ../../main.tex
\section{Results}\label{sec:artificial_data_results}
The results of all the data sets are provided in \Cref{tab:results_artificial}, together with the used parameters.
For each data set it shows the high and low thresholds used in the \gls{rt} based change detection method.
During the post-processing all detected change points within a certain \emph{closeness} range are merged, for which the value differs per data set.
The difference between the actual and final detected change points are expressed as an offset.
The data sets were processed with different window lengths and $\sigma$ value for the \gls{rbf} kernel.

\begin{table}
  \centering
  \caption[Results artificial data sets]{Parameter settings and results of the artificial data sets.}
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|}
    \cline{2-5}
    \multicolumn{1}{l|}{} & Set 1 & Set 2 & Set 3 & Set 4 \\
    \hline
    Window length & 50 & 100 & 50 & 50 \\
    \hline
    Sigma of \gls{rbf} & 13 & 13 & 15 & 13 \\
    \hline
    High threshold & 1.6 & 1.6 & 1.5 & 2.2 \\
    \hline
    Low threshold & 0.1 & 0.1 & 0.5 & 0.1 \\
    \hline
    Closeness & 10 & 10 & 10 & 50 \\
    \hline
    \hline
    $\gamma(Y)$ & 0 & 0.1 & 0.1 & 0.1 \\
    \hline
    $d_{avg}$ & 2.27 & 6.18 & 0.64 & 15.36 \\
    \hline
    $std(d_{avg})$ & 1.19 & 7.94 & 0.92 & 17.70 \\
    \hline
  \end{tabulary}
  \label{tab:results_artificial}
\end{table}

>>>>

% !TEX root = ../../main.tex
\section{Results}\label{sec:artificial_data_results}
The results of all the data sets are provided in \Cref{tab:results_artificial}, together with the used parameters.
For each data set it shows the high and low thresholds used in the \gls{rt} based change detection method.
During the post-processing all detected change points within a certain proximity $\delta$ are merged, for which the value differs per data set.
The difference between the actual and final detected change points are expressed as an offset.
The data sets were processed with different window lengths and $\sigma$ value for the \gls{rbf} kernel.

\begin{table}
  \centering
  \caption[Results artificial data sets]{Parameter settings and results of the artificial data sets.
  The table shows the \gls{far} $\gamma$, average delay $d_{avg}$ and its spread, using the standard deviation.
  Low values for the results are better.}
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|}
    \cline{2-5}
    \multicolumn{1}{l|}{} & Set 1 & Set 2 & Set 3 & Set 4 \\
    \hline
    Window length & 50 & 100 & 50 & 50 \\
    \hline
    Sigma of \gls{rbf} & 13 & 13 & 15 & 13 \\
    \hline
    High threshold & 1.6 & 1.6 & 1.5 & 2.2 \\
    \hline
    Low threshold & 0.1 & 0.1 & 0.5 & 0.1 \\
    \hline
    $\delta$ & 10 & 10 & 10 & 50 \\
    \hline
    \hline
    $\gamma(Y)$ & 0 & 0.1 & 0.1 & 0.1 \\
    \hline
    $d_{avg}$ & 2.27 & 6.18 & 0.64 & 15.36 \\
    \hline
    $std(d_{avg})$ & 1.19 & 7.94 & 0.92 & 17.70 \\
    \hline
  \end{tabulary}
  \label{tab:results_artificial}
\end{table}

### 2014-01-20 Chapters/Chapter6/results.tex
Updates

% !TEX root = ../../main.tex
\section{Results}\label{sec:real_world_results}
In this section we will provide the results of our methods \gls{ocs-hats} applied to the real-world data sets and discuss the quality of the solution.
As stated above, we will use the objective quality metrics as used in \Cref{sec:artificial_data_quality_metrics}.
That will be in the form of a tabular overview of the (manually set) best meta-parameters and results, expressed in \gls{far} $\gamma$ and average delay $d_{avg}$ (following \Cref{sec:artificial_data_results}).
Furthermore, we have anaylized the results from an emperical point of view, since the problem of finding change points in human activities is ambiguous.
For the sake of brevity we excluded those observations from this chapter and instead xthey can be found in \Cref{AppendixA}.

@@

\begin{table}
  \centering
  \caption[Results real world runs]{Results of the real-world data sets. The used parameters are: window length = $50$, $\sigma = 13$, $th_{high} = 1.2$, $th_{low} = 0.8$}
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c||c|}
    \cline{2-9}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 & Average \\
    \hline
    $\gamma(Y)$ & 0.1 & 0.2 & 0.14 & 0.37 & 0.29 & 0.64 & 0.57 & 0.33 \\
    \hline
    $d_{avg}$ & 0.52 & 0.85 & 0.93 & 0.54 & 0.69 & 0.51 & 0.32 & 0.62\\
    \hline
    $std(d_{avg})$ & 0.71 & 0.31 & 0.68 & 0.37 & 0.50 & 0.44 & 0.35 & 0.48 \\
    \hline
  \end{tabulary}
  \label{tab:results_final_real_world}
\end{table}

>>>>

% !TEX root = ../../main.tex
\section{Results}\label{sec:real_world_results}
In this section we will provide the results of our methods \gls{ocs-hats} applied to the real-world data sets and discuss the quality of the solution.
As stated above, we will use the objective quality metrics as used in \Cref{sec:artificial_data_quality_metrics}.
That will be in the form of a tabular overview of the (manually set) best meta-parameters and results, expressed in \gls{far} $\gamma$ and average delay $d_{avg}$ (following \Cref{sec:artificial_data_results}).
Furthermore, we have analyzed the results from an empirical point of view, since the problem of finding change points in human activities is ambiguous.
For the sake of brevity we excluded those observations from this chapter; they can be found in \Cref{AppendixA}.

@@

\begin{table}
  \centering
  \caption[Results real world runs]{Results of the real-world data sets. The used parameters are: window length = $50$, $\sigma = 13$, $th_{high} = 1.2$, $th_{low} = 0.8$, $\delta = 0.7$.
  The table shows the \gls{far} $\gamma$, average delay $d_{avg}$ and its spread, using the standard deviation.
  Low values are better.
  }
  \begin{tabulary}{\textwidth}{|l|c|c|c|c|c|c|c||c|}
    \cline{2-9}
    \multicolumn{1}{l|}{} & Run 1 & Run 2 & Run 3 & Run 4 & Run 5 & Run 6 & Run 7 & Average \\
    \hline
    $\gamma(Y)$ & 0.1 & 0.2 & 0.14 & 0.37 & 0.29 & 0.64 & 0.57 & 0.33 \\
    \hline
    $d_{avg}$ & 0.52 & 0.85 & 0.93 & 0.54 & 0.69 & 0.51 & 0.32 & 0.62\\
    \hline
    $std(d_{avg})$ & 0.71 & 0.31 & 0.68 & 0.37 & 0.50 & 0.44 & 0.35 & 0.48 \\
    \hline
  \end{tabulary}
  \label{tab:results_final_real_world}
\end{table}

### 2014-01-20 Chapters/Chapter7.tex
Updates

This research has applied \gls{occ} methods to inertial sensor data, recorded during the performance of various human activities, in order to create a temporal segmentation of those recordings.
The goal was to find the change points between activities, assuming that it will aid our understanding of the sensor values.
To do so, we used the \gls{svdd} algorithm by Tax~\cite{tax1999support}, following the method of applying it to a sliding window of data, as done by Camci~\cite{camci2010change}.
From these methods we have created our own method \gls{ocs-hats} and made it puclibly available \cite{vlasveld2014hats}, which is a slightly modified implemention of \gls{svcpd} by Camci~\cite{camci2010change} applied to \gls{har} data.
% Instead of using both the information whether a new data point is an outlier and the radius of the hypersphere to indicate change, we only used the latter model properties.
An increase of the radius of the constructed hypersphere, which encloses the data objects and increases with heterogeneous segments of data, is extracted and used for indication of change.

>>>>

This research has applied \gls{occ} methods to inertial sensor data, recorded during the performance of various human activities, in order to create a temporal segmentation of those recordings.
The goal was to find the change points between activities, assuming that it will aid our understanding of the sensor values.
To do so, we used the \gls{svdd} algorithm by Tax~\cite{tax1999support}, following the method of applying it to a sliding window of data, as done by Camci~\cite{camci2010change}.
From these methods we have created our own method \gls{ocs-hats} and made it publicly available \cite{vlasveld2014hats}, which is a slightly modified implementation of \gls{svcpd} by Camci~\cite{camci2010change} applied to \gls{har} data.
% Instead of using both the information whether a new data point is an outlier and the radius of the hypersphere to indicate change, we only used the latter model properties.
An increase of the radius of the constructed hypersphere, which encloses the data objects and increases with heterogeneous segments of data, is extracted and used for indication of change.
